Large-eddy simulations of the ice-shelf oceanic boundary layer

### 2021-04-19 main.tex
Updates from Overleaf

The time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a). During high-melt periods, the thermal exchange coefficient evaluated using a parameterization, is about 0.006 for all thermal driving values, less than the constant value of 0.011 reported in Jenkins et al. (2010) and commonly-used elsewhere, due to accounting for the degree of stratification. The time-averaged value decreases somewhat in the high thermal driving cases due to pronounced periods of low melt (Figure Gamma T vs. thermal driving). 
%The constant flux layer is ~2m.

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/gamma_T__e_res__dslope_tlim52.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
    \end{minipage}%    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope}
    \label{fig:melt_sensitivity}
\end{figure}

>>>>

The time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a). The thermal exchange coefficient as computed using Equation \ref{eq:gamma} during the last 12 hours of the simulations is between 0.005 and 0.006 for the simulated range of thermal driving values. The time-averaged value decreases somewhat in the high thermal driving cases due to pronounced periods of low melt as TKE declines with increasing stratification.

These values are less than the thermal exchange coefficient of 0.011 derived from observations in Jenkins et al. (2010). During the first 12 hours of the simulation, simulated thermal exchange coefficients are 0.008 due to weaker stratification near the interface and higher friction velocities due to greater TKE.

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4.1cm 0 0},clip,width=\textwidth]{Figures/gammaT_dT_tav12_zlim2.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/gamma_T__us__dslope_tav12_tlim52.png}
    \end{minipage}
    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope. (c) Thermal exchange coefficient vs. far-field thermal driving for thermal driving simulations. (d) Thermal exchange coefficient vs. friction velocity for sloped simulations.}
    \label{fig:melt_sensitivity}
\end{figure}
